Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-02-22 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
Notation.

\subsection{Near linear proportionality between $m$, $c$, and $\ell$} \label{subsec_theoretic_linearity}

@@

As explained in Section~\ref{subsec_theoretic_linearity}, when $c$ is large enough, there is a near linear proportionality between $m$, $\frac{l}{S}$ (length-scale $l$ relative to the half range of the input domain $S$) and $c$. To obtain practical numerical functions that can be used to guide the selection of these parameters, we have empirically derived the practically useful constant terms. We require a lower bound for $c$ of $c \geq 1.2$ such that the equations below are precise enough for practical application.

>>>>

\subsection{Near linear proportionality between $m$, $c$ and $\ell$} \label{subsec_theoretic_linearity}

@@

As explained in Section~\ref{subsec_theoretic_linearity}, when $c$ is large enough, there is a near linear proportionality between $m$, $\frac{\ell}{S}$ (length-scale $\ell$ relative to the half range of the input domain $S$) and $c$. To obtain practical numerical functions that can be used to guide the selection of these parameters, we have empirically derived the practically useful constant terms. We require a lower bound for $c$ of $c \geq 1.2$ such that the equations below are precise enough for practical application.
